### 2021-03-18 README.Rmd
tweaks to overview in readme

The Australian Institute of Marine Science (AIMS) has a long tradition in
measuring and monitoring a series of environmental parameters along the
tropical coast of Australia. These parameters include long-term record of sea
surface temperature, wind characteristics, atmospheric temperature, pressure,
chlorophyll-a data, among many others. The AIMS Data Centre team has recently
developed the [AIMS Data Platform API][1] which is a *REST API* providing
JSON-formatted data to users. `dataaimsr` is an **R package** written to
allow users to communicate with the AIMS Data Platform API using an API key
and a few convenience functions to interrogate and understand the datasets
that are available to download.

@@

>>>>

The Australian Institute of Marine Science (AIMS) has a long tradition in
measuring and monitoring a series of environmental parameters along the
tropical coast of Australia. These parameters include long-term record of sea
surface temperature, wind characteristics, atmospheric temperature, pressure,
chlorophyll-a data, among many others. The AIMS Data Centre team has recently
developed the [AIMS Data Platform API][1] which is a *REST API* providing
JSON-formatted data to users. `dataaimsr` is an **R package** written to
allow users to communicate with the AIMS Data Platform API using an API key
and a few convenience functions to interrogate and understand the datasets
that are available to download. In doing so, it allows the user to
fully explore these datasets in R in whichever capacity they want (e.g.
data visualisation, statistical analyses, etc). The package itself contains
a `plot` method which allows the user to plot summaries of the different types
of dataset made available by the API. Below we provide a brief context about
the existing [Datasets][#datasets] that can be explored through `dataaimsr`.

@@

## Datasets
